---
title: "R Notebook - Company information and control variables"
output: html_notebook
author: "Frederik Heijbroek"
---

# Overview

This R Notebook is for finding and data pre-processing of the control variables.

# Libraries

Loading packages

```{r}
if (!require("httr")) install.packages("httr")
if (!require("jsonlite")) install.packages("jsonlite")
if (!require("dplyr")) install.packages("dplyr")
```

```{r}
library(httr)
library(jsonlite)
library(dplyr)
```

# Symbol list

```{r}
Transcripts_symbols
```


# 2. Extracting control variables: company information and financials

**Financial Modeling Prep (FMP)** 

*Key*

```{r}
# Financial Modeling Prep API key
api_key_FMP <- "27d166fe97887d83743f46bd83773b2e"
```

https://site.financialmodelingprep.com/developer/docs/pricing/


## 2.1 General company information - FMP

**Function for extracting general company information**

```{r}
# Function to get company profile information for a symbol
func_company_profile <- function(symbol, api_key_FMP) {
  base_url <- "https://financialmodelingprep.com/api/v3/"
  endpoint <- "profile"
  
  query_url <- paste0(base_url, endpoint, "/", symbol, "?apikey=", api_key_FMP)
  response <- GET(query_url)
  
  if (http_status(response)$category == "Success") {
    content <- fromJSON(content(response, "text", encoding = "UTF-8"))
    
    # Convert the content to a data frame
    company_profile <- data.frame(content)
    
    return(company_profile)
  } else {
    warning(paste0("Failed to fetch data for ", symbol))
    return(NULL)
  }
}

```

Looping through the symbols universe

```{r}
# Retrieve company profile data for all symbols
company_profiles_list_transcripts <- lapply(Transcripts_symbols, function(symbol) {
  cat("Fetching data for", symbol, "\n")
  company_profile <- func_company_profile(symbol, api_key_FMP)
  
  # Add a sleep time (2 seconds) to avoid hitting the API rate limits
  Sys.sleep(0.5)
  
  return(company_profile)
})

```

```{r}
# Combine the company profile data frames
company_profiles_df_transcripts <- do.call(rbind, company_profiles_list_transcripts)

```

### Find list with exchange market names 

**exchange markets**

```{r}
unique_exchange <- unique(company_profiles_df_transcripts$exchangeShortName)
unique_exchange

```

## 2.2 Financial information - FMP

**Function to retrieve financial information data**

```{r}
# Function to get historical financial ratios for a symbol
func_financial_ratios <- function(symbol, api_key_FMP) {
  base_url <- "https://financialmodelingprep.com/api/v3/"
  endpoint <- "ratios"

  # Calculate the dates for the last five years
  to_date <- Sys.Date()
  from_date <- to_date - 7 * 365

  # Include the period parameter and set it to "quarter"
  query_url <- paste0(base_url, endpoint, "/", symbol, "?period=quarter&apikey=", api_key_FMP)
  response <- GET(query_url)

  if (http_status(response)$category == "Success") {
    content <- fromJSON(content(response, "text", encoding = "UTF-8"))

    # Convert the content to a data frame
    financial_ratios <- data.frame(content)

    return(financial_ratios)
  } else {
    warning(paste0("Failed to fetch data for ", symbol))
    return(NULL)
  }
}

```

```{r}
# Retrieve historical financial ratios data for all symbols
financial_ratios_list_transcripts <- lapply(Transcripts_symbols, function(symbol) { # symbol universe
  cat("Fetching data for", symbol, "\n")
  financial_ratios <- func_financial_ratios(symbol, api_key_FMP)
  
  # Add a sleep time (0.3 seconds) to avoid hitting the API rate limits
  Sys.sleep(0.3)
  
  return(financial_ratios)
})

```

```{r}
# Combine the financial ratios data frames
financial_ratios_df_transcripts <- do.call(rbind, financial_ratios_list_transcripts)
financial_ratios_df_transcripts <- financial_ratios_df_transcripts[financial_ratios_df_transcripts$date > (Sys.Date() - 7*365), ]

```

**Test API functioning**

```{r}
symbol <- "MSFT"
base_url <- "https://financialmodelingprep.com/api/v3/"
endpoint <- "ratios"
query_url <- paste0(base_url, endpoint, "/", symbol, "?apikey=", api_key_FMP)
response <- GET(query_url)
print(http_status(response))
print(content(response, "text", encoding = "UTF-8"))

```


## 2.3 Earnings report information - FMP

```{r}
func_earnings_report <- function(symbol, api_key_FMP) {
  base_url <- "https://financialmodelingprep.com/api/v3/"
  endpoint <- "income-statement"

  # Calculate the dates for the last seven years
  to_date <- Sys.Date()
  from_date <- to_date - 7 * 365

  # Convert dates to character and include the period parameter set to "quarter"
  query_url <- paste0(base_url, endpoint, "/", symbol, "?from=", as.character(from_date), "&to=", as.character(to_date), "&period=quarter&apikey=", api_key_FMP)
  response <- GET(query_url)

  if (http_status(response)$category == "Success") {
    content <- fromJSON(content(response, "text", encoding = "UTF-8"))

    # Convert the content to a data frame
    earnings_report <- data.frame(content)

    return(earnings_report)
  } else {
    warning(paste0("Failed to fetch data for ", symbol))
    return(NULL)
  }
}

```

```{r}
# Retrieve historical earnings report data for all symbols
earnings_report_list_transcripts <- lapply(Transcripts_symbols, function(symbol) { # symbol universe
  cat("Fetching data for", symbol, "\n")
  earnings_report <- func_earnings_report(symbol, api_key_FMP)
  
  # Add a sleep time (0.5 seconds) to avoid hitting the API rate limits
  Sys.sleep(0.5)
  
  return(earnings_report)
})

```

```{r}
# Combine the earnings report data frames
earnings_report_df_transcripts <- do.call(rbind, earnings_report_list_transcripts)
earnings_report_df_transcripts <- earnings_report_df_transcripts[earnings_report_df_transcripts$date > (Sys.Date() - 7*365), ]
```

```{r}
length(unique(earnings_report_df_transcripts$symbol)) # 363 unique companies
```


## 2.4 EPS data Alpha vantage

```{r}
# Alpha Vantage API key
api_key_AV <- "ENIQNI8C67KARI4G"

```

https://www.alphavantage.co/documentation/

Function to retrieve company information data from Alpha Vantage
- 500 requests / day 


```{r}
# Define the function to get EPS data
func_eps <- function(symbol, api_key_AV) {
  
  # Define the API URL
  api_url <- paste0('https://www.alphavantage.co/query?function=EARNINGS&symbol=', symbol, '&apikey=', api_key_AV)
  
  # Get the data from the API
  response <- GET(api_url)
  
  if (http_status(response)$category == "Success") {
    # Parse the JSON content from the API response
    content <- fromJSON(content(response, "text", encoding = "UTF-8"))

    # Convert the quarterly earnings data to a data frame and add symbol column
    earnings_df <- data.frame(content$quarterlyEarnings)
    
    if(nrow(earnings_df) > 0) {
      earnings_df$symbol <- symbol
      # Reorder columns to put symbol first
      earnings_df <- earnings_df[, c("symbol", setdiff(names(earnings_df), "symbol"))]
    } else {
      warning(paste0("No data available for ", symbol))
    }
    
    return(earnings_df)
  } else {
    warning(paste0("Failed to fetch data for ", symbol))
    return(NULL)
  }
}

```


```{r}
# Retrieve earnings data for all symbols
eps_list <- lapply(Transcripts_symbols, function(symbol) {
  
  cat("Fetching data for", symbol, "\n")
  earnings_df <- func_eps(symbol, api_key_AV)
  
  # Add a sleep time (12 seconds) to avoid hitting the API rate limits
  Sys.sleep(12)
  
  return(earnings_df)
})

```

```{r}
# Bind all the earnings data frames together
eps_df <- do.call(rbind, eps_list)

eps_df <- eps_df[eps_df$fiscalDateEnding > (Sys.Date() - 7*365), ]

# Print the earnings dataframe
print(eps_df)

```

```{r}
eps_df %>% 
  group_by(symbol) %>% 
  summarise(count = n()) %>% 
  nrow()

```


## 2.5 Data transformations

### Finacial ratio's 

```{r}
financial_ratios_df_transcripts <- financial_ratios_df_transcripts %>% 
  mutate(period_n = as.numeric(str_extract(period, "\\d")))
```

```{r}
# Change data types
# financial_ratios_df_transcripts$acceptedDate <- as.POSIXct(financial_ratios_df_transcripts$acceptedDate, format = "%Y-%m-%d %H:%M:%S")
# financial_ratios_df_transcripts$acceptedDate <- as.Date(force_tz(financial_ratios_df_transcripts$acceptedDate), tzone = "US/Eastern")

financial_ratios_df_transcripts$date <- as.Date(financial_ratios_df_transcripts$date)
```


### Earnings report data

```{r}
# Change data types
earnings_report_df_transcripts$acceptedDate <- as.POSIXct(earnings_report_df_transcripts$acceptedDate, format = "%Y-%m-%d %H:%M:%S")
earnings_report_df_transcripts$acceptedDate <- as.Date(force_tz(earnings_report_df_transcripts$acceptedDate), tzone = "US/Eastern")

earnings_report_df_transcripts$date <- as.Date(earnings_report_df_transcripts$date)
earnings_report_df_transcripts$fillingDate <- as.Date(earnings_report_df_transcripts$fillingDate)

# Split `calendarYear` column
earnings_report_df_transcripts <- earnings_report_df_transcripts %>% 
  mutate(quarter = as.numeric(str_extract(period, "\\d")),
         year = as.numeric(calendarYear)) 

```

### EPS data

```{r}
eps_df$fiscalDateEnding <- as.Date(eps_df$fiscalDateEnding)
eps_df$reportedDate <- as.Date(eps_df$reportedDate)
reportedDate

```

**Save and load the data**

```{r}
save(financial_ratios_df_transcripts,
     company_profiles_df_transcripts,
     earnings_report_df_transcripts,
     eps_df,
     file = "RData/Controls.RData")

```

```{r}
load("RData/Controls.RData")
```

## 2.6 Merging steps 

See `Stocks` notebook 

