---
title: "R Notebook - Stock data"
output: html_notebook
author: "Frederik Heijbroek"
---

# Overview

This R Notebook is for finding and data pre-processing of the stock price data

# Libraries

```{r}
if (!require("quantmod")) install.packages("quantmod")
if (!require("dplyr")) install.packages("dplyr")
if (!require("magrittr")) install.packages("magrittr")
if (!require("readr")) install.packages("readr")
if (!require("data.table")) install.packages("data.table")
if (!require("tidyquant")) install.packages("tidyquant")
if (!require("lubridate")) install.packages("lubridate")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("progress")) install.packages("progress")
if (!require("tidyr")) install.packages("tidyr")

```


```{r}
library(quantmod)
library(dplyr)
library(magrittr)
library(readr)
library(data.table)
library(tidyquant)
library(lubridate)
library(ggplot2)
library(progress)
library(tidyr)
```

# Symbol list

from stock_price notebook

# 3. Stock price using Yahoo Finance

**Function to fetch stock data**

The following function extracts the daily stock price data for companies from Yahoo Finance. `Quantmod` library is used to fetch all the stock information.

```{r}
# Function to fetch daily stock data 
func_stock_data <- function(symbol, start_date, end_date) {
  stock_data <- tryCatch({
    getSymbols(Symbols = symbol, 
               src = "yahoo", 
               from = start_date, 
               to = end_date, 
               auto.assign = FALSE)
  }, error = function(e) {
    NULL
  })
  
  if (!is.null(stock_data)) {
    stock_data <- as.data.frame(stock_data)
    stock_data$Symbol <- symbol
    
    # Handle date conversion errors
    stock_data$Date <- tryCatch({
      as.Date(rownames(stock_data))
    }, error = function(e) {
      warning(paste("Error converting dates for", symbol))
      return(NULL)
    })
    
    if (is.null(stock_data$Date)) {
      return(NULL)
    }
    
    rownames(stock_data) <- NULL
    colnames(stock_data) <- c("Open", "High", "Low", "Close", "Volume", "Adjusted", "Symbol", "Date")
    stock_data <- stock_data %>%
     dplyr::select(Date, Symbol, Open, High, Low, Close, Volume)
  }
  
  return(stock_data)
}
```

We are interested in the daily stock price information from the last 7 years. The function below sets the sample period for which the daily stock price data is fetched. 

```{r}
start_date <- Sys.Date() - 365 * 7 # 7 years ago from today
end_date <- Sys.Date() - 1 # Yesterday
```

test function

```{r}
# Test function for AAPL
getSymbols("AAPL",
           src = "yahoo",
           from = start_date,
           to = end_date,
           auto.assign = FALSE)

AAPL_try <- func_stock_data("AAPL", start_date, end_date)
rm(AAPL_try)
```

We fetch the stock data for the symbol universe, `Transcripts_symbols`, and organise the data in a data frame.  

1761 trading days in last 7 years.

```{r}
# extract stock data for the 447 companies out of the transcripts data of the last 7 years
stock_data_list <- lapply(Transcripts_symbols, function(symbol) { 
  cat("Fetching data for", symbol, "\n")
  stock_data <- func_stock_data(symbol, start_date, end_date)
  return(stock_data)
})

stock_data_df_transcripts <- do.call(rbind, stock_data_list) 

```

```{r}
Transcripts_symbols
```


## 3.2 Exploratory analysis

**Unique companies stock info**

67 companies with missing stock information. 380/447 complete

```{r}
stock_data_df_transcripts %>% 
  group_by(Symbol) %>% 
  summarise(count = n()) %>% 
  nrow()

# str(stock_data_df_transcripts)

```

380

There are some missing values for the daily stock price of a few companies. Remove symbols with fewer than 150 observations of daily stock data.

```{r}
# Filter out symbols with fewer than 200 observations
stock_data_filtered <- stock_data_df_transcripts %>%
  group_by(Symbol) %>%
  filter(n() >= 200) %>%
  ungroup()

# Print the number of rows and the structure of the filtered data frame
# str(stock_data_filtered)

# Print the number of unique symbols in the filtered data frame
length(unique(stock_data_filtered$Symbol)) ## 69 companies removed from original data set

```

378 companies with daily stock data. 2 companies removed from the original data set, which have no or too few observations.

## 3.3 Data transformations

Make new columns to calculate daily and two day change

```{r}
stock_data_df_transcripts_1 <- stock_data_filtered %>% 
  mutate(Return = Close - lag(Close),
         Return_rate = (Close - lag(Close)) / lag(Close))

print(stock_data_df_transcripts_1)
```

**Removing NA's** 

```{r}
summary(stock_data_df_transcripts_1)

# Remove rows with NA values using complete.cases()
stock_data_df_transcripts_1 <- stock_data_df_transcripts_1[complete.cases(stock_data_df_transcripts_1), ]
summary(stock_data_df_transcripts_1)

```

## 3.4 Market indices daily prices

**Function to fetch daily market prices**

```{r}
func_market_index_data <- function(indices, start_date, end_date) {
  index_data <- lapply(indices, function(index) {
    data <- tryCatch(
      tq_get(index, from = start_date, to = end_date, get = "stock.prices"),
      error = function(e) {
        message("Error getting data for index: ", index)
        return(NULL)
      }
    )
    return(data)
  })

  names(index_data) <- indices

  return(index_data)
}

```

Ticker	Market Name
^GSPC	S&P 500 (U.S.)
^IXIC	NASDAQ Composite (U.S.)
^NYA	NYSE Composite (U.S.)
^FTSE	FTSE 100 (UK)
^GDAXI	DAX 30 (Germany)
^FCHI	CAC 40 (France)
^IBEX	IBEX 35 (Spain)
^FTMIB	FTSE MIB (Italy) --> error
^AEX	AEX Index (Netherlands)
^OMX	OMX Stockholm 30 (Sweden)
^N225	Nikkei 225 (Japan)
^HSI	Hang Seng Index (Hong Kong)
^SSEC	Shanghai Composite (China)  
^BSESN	S&P BSE SENSEX (India)
^ASX	ASX 200 (Australia)
^BVSP	Bovespa (Brazil)
^TSX	S&P/TSX Composite (Canada) 


```{r}
# Market indeces / proxies 
market_indices <- c("^GSPC", "^NYA", "^IXIC")

start_date <- Sys.Date() - 365 * 7 # 7 years ago from today
end_date <- Sys.Date() - 1 # Yesterday

market_index_data <- func_market_index_data(market_indices, start_date, end_date)
market_index_df <- do.call(rbind, market_index_data)

# Change column names
new_column_names <- c("Symbol", "Date", "Open", "High", "Low", "Close", "Volume", "Adjusted")
colnames(market_index_df) <- new_column_names

```

### Data transformations 

```{r}
market_index_df_1 <- market_index_df %>% 
  mutate(Return = Close - lag(Close),
         Return_rate = (Close - lag(Close)) / lag(Close))

```


--------------------------------------------------------------------------------

## 3.4 Stock prices + Company general information - Merge 

Adding to the stock data the exchange market column from the company general information data frame, notebook: (`company_financials.Rmd`). 

```{r}
stock_data_df_transcripts_2 <- stock_data_df_transcripts_1 %>% 
  left_join(company_profiles_df_transcripts, by = c("Symbol" = "symbol")) %>% 
  select(Date, Symbol, Open, High, Low, Close, Volume, Return, Return_rate, 
         exchange, exchangeShortName)

# Change the short name
stock_data_df_transcripts_2 <- stock_data_df_transcripts_2 %>% 
  mutate(marketSymbol = case_when(
    exchangeShortName == "NYSE" ~ "^NYA",
    exchangeShortName == "NASDAQ" ~ "^IXIC",
    exchangeShortName == "AMEX" ~ "^NYA",
    exchangeShortName == "PNK" ~ "^NYA",
    TRUE ~ exchangeShortName
  ))

```

## 3.5 Exchange market (Proxy) daily prices + stock daily prices - Merge

Merge stock returns and market returns data frame

```{r}
# Merge stock returns and market returns
stock_data_df_transcripts_final <- stock_data_df_transcripts_2 %>%
  inner_join(market_index_df_1, by = c("Date" = "Date", "marketSymbol" = "Symbol"), suffix = c("_stock", "_market"))

# str(stock_data_df_transcripts_final)
print(stock_data_df_transcripts_final)

rm(merged_returns,
   stock_data_df_transcripts_1,
   stock_data_df_transcripts_2,
   stock_data_df_transcripts_3,
   market_index_df_1
   )

```

```{r}
summary(stock_data_df_transcripts_final)

# Remove rows with NA values using complete.cases()
stock_data_df_transcripts_final_noNA <- stock_data_df_transcripts_final[complete.cases(stock_data_df_transcripts_final), ]
```

### subset for testing

```{r}
selected_symbols <- c("FDX", "AAPL", "A")

merged_returns_selected <- merged_returns %>% 
  filter(Symbol %in% selected_symbols)

print(merged_returns_selected)
```


## 3.6 Find Abnormal returns

**Function to find abnormal returns**

Function below takes about 30 - 45 minutes 

```{r}
func_abnormal_returns <- function(data, estimation_window) {
  # Initialize new columns in the data frame with NA values
  data <- data %>%
    mutate(Alpha = NA, Beta = NA, Expected_Return = NA, Abnormal_Return = NA,
           Cumulative_Abnormal_Return_2day = NA)
  
  # Create a progress bar
  # pb <- progress_bar$new(total = nrow(data) - estimation_window - 1, format = "[:bar] :percent :elapsed")

  # Loop through the data frame starting from the row after the estimation window
  for (i in (estimation_window + 1):(nrow(data) - 1)) {
    # Extract the estimation data based on the estimation window
    estimation_data <- data[(i - estimation_window):(i - 1), ]
    
    # Run a linear regression to estimate the relationship between stock and market returns
    model <- lm(Return_rate_stock ~ Return_rate_market, data = estimation_data)
    
    # Extract alpha and beta coefficients from the linear regression model
    alpha <- coef(model)["(Intercept)"]
    beta <- coef(model)["Return_rate_market"]
    
    # Assign alpha and beta values to the corresponding rows in the data frame
    data$Alpha[i] <- alpha
    data$Beta[i] <- beta
    
    # Calculate the expected return and abnormal return for the current day
    data$Expected_Return[i] <- alpha + beta * data$Return_rate_market[i]
    data$Abnormal_Return[i] <- data$Return_rate_stock[i] - data$Expected_Return[i]
    
    # Update the progress bar
    # pb$tick()
    
  }
  
  # Calculate the cumulative abnormal return for a two-day period in a separate loop
  for (i in (estimation_window + 1):(nrow(data) - 1)) {
    data$Cumulative_Abnormal_Return_2day[i] <- data$Abnormal_Return[i] + data$Abnormal_Return[i + 1]
  }

  # Return the modified data frame with the calculated values
  return(data)
}

```

```{r}
head(stock_data_df_transcripts_final)
summary(stock_data_df_transcripts_final)
```


```{r}
# Group the data by Symbol and apply the function to calculate abnormal returns, Alpha, and Beta using a 100-day estimation window
abnormal_returns_data_100 <- stock_data_df_transcripts_final %>% 
  group_by(Symbol, exchange) %>%
  group_modify(~ func_abnormal_returns(.x, estimation_window = 100))

# Group the data by Symbol and apply the function to calculate abnormal returns, Alpha, and Beta using a 200-day estimation window
abnormal_returns_data_50 <- stock_data_df_transcripts_final %>% 
  group_by(Symbol, exchange) %>%
  group_modify(~ func_abnormal_returns(.x, estimation_window = 50))

# Group the data by Symbol and apply the function to calculate abnormal returns, Alpha, and Beta using a 100-day estimation window
abnormal_returns_data_100 <- stock_data_df_transcripts_final %>% 
  group_by(Symbol, exchange) %>%
  group_modify(~ func_abnormal_returns(.x, estimation_window = 150))

# Examine the abnormal returns data
abnormal_returns_data_100
abnormal_returns_data_200
abnormal_returns_data_50
```


--------------------------------------
############ Move Here ###############
--------------------------------------

```{r}
load("RData/Abnormal_Returns")
```



# Merge 

## 3.7 Transcript data + stock data - Merge

Merge transcript data and stock data

**Transcript data & Stock data**

Here we test with different stock estimation windows: 
- 50
- 100
- 200

```{r}
joined_transcripts_stock <- unique_company_transcript_complete %>% 
  left_join(abnormal_returns_data_100, by = c("symbol" = "Symbol", "transcriptDate" = "Date")) # abnormal_returns_data_full, stock_data_df_transcripts

# Main and Q&A split
joined_transcripts_stock_section <- unique_company_transcript_section_complete_long %>% 
  left_join(abnormal_returns_data_100, by = c("symbol" = "Symbol", "transcriptDate" = "Date")) # abnormal_returns_data_full, stock_data_df_transcripts


print(joined_transcripts_stock)


# Find missing rows and remove from data frame

missing_rows <- joined_transcripts_stock[!complete.cases(joined_transcripts_stock), ] # 1091 missing rows 
joined_transcripts_stock <- joined_transcripts_stock[complete.cases(joined_transcripts_stock), ]
joined_transcripts_stock_section <- joined_transcripts_stock_section[complete.cases(joined_transcripts_stock_section), ]


# save(stock_data_df_transcripts,
#     joined_transcripts_stock,
#     file = "RData/Stock_data.RData")
```

## 3.8 Company profile data + Transcript/Stock data - Merge 

```{r}
# Make selection of the general company information
company_profiles_df_transcripts_select <- company_profiles_df_transcripts %>% 
  select(symbol, mktCap, industry, sector, country)

# Merge with the transcript and stock data frame
joined_transcripts_stock_profile <- joined_transcripts_stock %>% 
  left_join(company_profiles_df_transcripts_select, by = c("symbol" = "symbol"))

# Merge with the transcript and stock data frame (Main and Q&A split)
joined_transcripts_stock_profile_section <- joined_transcripts_stock_section %>% 
  left_join(company_profiles_df_transcripts_select, by = c("symbol" = "symbol"))

print(joined_transcripts_stock_profile)
print(joined_transcripts_stock_profile_section)


```


--------------

## 3.9 Earnings report data, EPS & Financial ratio's - Merge

```{r}
# Make selection of the earnings report data
earnings_report_df_transcripts_select <- earnings_report_df_transcripts %>% 
  select(date, fillingDate, acceptedDate, symbol, year, quarter, revenue, eps)

# Make selection of the financials data
financial_ratios_df_transcripts_select <- financial_ratios_df_transcripts %>% 
  select(date, symbol, period_n, currentRatio, returnOnAssets, returnOnEquity, debtRatio, capitalExpenditureCoverageRatio, priceToBookRatio)

```

```{r}
financial_ratios_df_transcripts_select <- financial_ratios_df_transcripts_select %>%
  filter(duplicated(symbol, date))

earnings_report_df_transcripts_select <- earnings_report_df_transcripts_select %>%
  filter(duplicated(symbol, date))

```

```{r}
# First join
merged_df <- earnings_report_df_transcripts_select %>% 
  left_join(eps_df, by = c("symbol" = "symbol", "date" = "fiscalDateEnding"))

# Identify rows with NA
na_rows <- is.na(merged_df$reportedEPS)
na_count <- sum(na_rows) #2476 missing rows

# Create a new dataframe for those rows with NAs
merged_df_na <- merged_df[na_rows, ] %>% 
  select(-reportedDate, -reportedEPS, -estimatedEPS, -surprise, -surprisePercentage)

# Perform second join on the new data frame
merged_df_na <- merged_df_na %>%
  left_join(eps_df, by = c("symbol" = "symbol", "fillingDate" = "reportedDate")) %>% 
  select(-fiscalDateEnding)

na_rows <- is.na(merged_df_na$reportedEPS)
na_count <- sum(na_rows) # 298 recovered, 2178 still missing

complete_df_na <- merged_df_na[complete.cases(merged_df_na), ]

complete_df_na <- complete_df_na %>% 
  select(date, symbol, reportedEPS, estimatedEPS, surprise, surprisePercentage)

merged_df <- merged_df %>% 
  select(-reportedDate) 

# First, join the two dataframes together
df_full <- left_join(merged_df, complete_df_na, by = c("symbol", "date"))

df_filled <- df_full %>%
  mutate(
    reportedEPS.x = ifelse(is.na(reportedEPS.x) & !is.na(reportedEPS.y), reportedEPS.y, reportedEPS.x),
    estimatedEPS.x = ifelse(is.na(estimatedEPS.x) & !is.na(estimatedEPS.y), estimatedEPS.y, estimatedEPS.x),
    surprise.x = ifelse(is.na(surprise.x) & !is.na(surprise.y), surprise.y, surprise.x),
    surprisePercentage.x = ifelse(is.na(surprisePercentage.x) & !is.na(surprisePercentage.y), surprisePercentage.y, surprisePercentage.x)
  )


df_final <- df_filled %>%
  select(-ends_with(".y"))

df_final <- df_final %>%
  rename_with(~ gsub("\\.x$", "", .x), ends_with(".x"))


# Identify rows with NA
na_rows <- is.na(df_final$reportedEPS)
na_count <- sum(na_rows) #2178 missing rows

df_final

```

```{r}
earnings_report_df_transcripts_select_eps <- df_final %>% 
  select(-fillingDate, -acceptedDate)

```

```{r}
rm(complete_df_na,
   df_filled,
   df_final,
   df_full,
   merged_df,
   merged_df_na,
   missing_rows)
```

### Earnings report & EPS + Financial ratio's 

```{r}
# Merge earnings report and financial ratio's data
joined_controls <- earnings_report_df_transcripts_select_eps %>% 
  full_join(financial_ratios_df_transcripts_select, by = c("symbol" = "symbol", "date" = "date")) %>% 
  select(-quarter)

# Find duplicates based on two keys
duplicates <- joined_controls[duplicated(paste(joined_controls$symbol, joined_controls$date)), ]
print(duplicates)

# Remove duplicates based on two keys
joined_controls <- joined_controls[!duplicated(paste(joined_controls$symbol, joined_controls$date)), ]
print(joined_controls)

```

## 3.10 Final data set: Controls (Earnings report & Financials) + Transcript/Stock/Profile data - Merge

```{r}
duplicated_rows_left <- joined_transcripts_stock_profile[duplicated(joined_transcripts_stock_profile[c("symbol", "year", "quarter")]), ]

```

period_n comes from the financial ratio's data. This period (quarter) is more accurate than the quarter column from the earnings report data. There are more matching earnings calls when using the period_n column.


-------------------------------

```{r}
# Merge earnings report data with transcript, stock and company information using `symbol`, `year` `quarter`
joined_transcripts_stock_profile_earnings <- joined_transcripts_stock_profile %>% 
  left_join(joined_controls, by = c("symbol" = "symbol", "year" = "year", "quarter" = "period_n")) %>% 
  select(-date)

# Merge earnings report data with transcript, stock and company information using `symbol`, `year` `quarter` (Main and Q&A split)
joined_transcripts_stock_profile_earnings_section <- joined_transcripts_stock_profile_section %>% 
  left_join(joined_controls, by = c("symbol" = "symbol", "year" = "year", "quarter" = "period_n")) %>% 
  select(-date)

# Print final data frame
print(joined_transcripts_stock_profile_earnings) # 7393 rows 
print(joined_transcripts_stock_profile_earnings_section)


```

```{r}
mismatched_rows <- joined_transcripts_stock_profile_earnings_section %>% filter(symbol != symbol_old)
```


### Cleaning final data frame 

**Remove NA's** 

```{r}
# Final data frame (with NA)
final_df_NA <- joined_transcripts_stock_profile_earnings
final_df_section_NA <- joined_transcripts_stock_profile_earnings_section

# Find rows with missing data
missing_rows <- joined_transcripts_stock_profile_earnings[!complete.cases(joined_transcripts_stock_profile_earnings), ]

# Count missing values in each row
missing_counts <- rowSums(is.na(joined_transcripts_stock_profile_earnings))

# Final data frame (No NA)
final_df <- joined_transcripts_stock_profile_earnings[complete.cases(joined_transcripts_stock_profile_earnings), ]
final_df_section <- joined_transcripts_stock_profile_earnings_section[complete.cases(joined_transcripts_stock_profile_earnings_section), ]

length(unique(final_df$transcriptID))

final_df %>% 
  group_by(symbol) %>% 
  summarise(count = n()) %>% 
  nrow()


# Check the result
print(final_df) # 7132 --> 6381

rm(duplicates,
   missing_rows,
   missing_counts)



```

**Saving and loading tidy data frames**

```{r}
save(joined_transcripts_stock_profile_earnings,
     final_df_section,
     final_df,
     file = "RData/final_df_20230605.RData")

```






