---
title: "R Notebook - Visualisations "
output: html_notebook
author: "Frederik Heijbroek"
---

# Overview

This R Notebook is for visualising the data

# Libraries

```{r}
if (!require("dplyr")) install.packages("dplyr")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("stargazer")) install.packages("stargazer")
if (!require("corrplot")) install.packages("corrplot")
if (!require("xtable")) install.packages("xtable")
if (!require("forcats")) install.packages("forcats")
if (!require("ggthemes")) install.packages("ggthemes")
if (!require("skimr")) install.packages("skimr")
if (!require("DescTools")) install.packages("DescTools")
if (!require("lmtest")) install.packages("lmtest")
```


```{r}
library(dplyr)
library(ggplot2)
library(stargazer)
library(corrplot)
library(xtable)
library(forcats)
library(ggthemes)
library(skimr)
library(DescTools)
library(lmtest)
```

```{r}
load("RData/final_df_20230605.RData")
```

# 4. Data visualisations and regression analysis

## 4.1 Summary statistics 

The original data set contains 8507 unique transcripts for 373 companies in the period of 2016 to 2023. The data is merged with company general information, stock price data, and data from quarterly earnings reports (EPS). After removing missing values, we keep 6381 transcripts that contain the full range of data. 

final df: 6,380 × 59

## 4.2 Data transformations


```{r}
# Change column names 
final_df_section <- final_df_section %>% 
  rename(AI_bigrams_Main = `count_AI_bigrams_MAIN SECTION`,
         AI_bigrams_QA = `count_AI_bigrams_Q&A SECTION`,
         AI_words_Main = `count_AI_words_MAIN SECTION`,
         AI_words_QA = `count_AI_words_Q&A SECTION`,
         RAI_bigrams_Main = `count_RAI_bigrams_MAIN SECTION`,
         RAI_bigrams_QA = `count_RAI_bigrams_Q&A SECTION`,
         RAI_words_Main = `count_RAI_words_MAIN SECTION`,
         RAI_words_QA = `count_RAI_words_Q&A SECTION`,
         AI_Main = `sum_AI_count_MAIN SECTION`,
         AI_QA = `sum_AI_count_Q&A SECTION`,
         RAI_Main = `sum_RAI_count_MAIN SECTION`,
         RAI_QA = `sum_RAI_count_Q&A SECTION`,
         CECR = capitalExpenditureCoverageRatio,
         CAR_2day = Cumulative_Abnormal_Return_2day,
         PriceToBookR = priceToBookRatio) %>% 
  mutate(AI = AI_Main + AI_QA, 
         RAI = RAI_Main + RAI_QA)

```

```{r}
final_df_section <- final_df_section %>% 
  select(transcriptID, companyName, symbol, eventName, quarterYear,
         year, quarter, transcriptDate, totalWordCount, AI_words_Main, AI_bigrams_Main, AI_words_QA,
         AI_bigrams_QA, RAI_words_Main, RAI_bigrams_Main, RAI_words_QA, RAI_bigrams_QA, AI_Main, AI_QA,
         RAI_Main, RAI_QA, AI, RAI, exchange, Open_stock, High_stock, Low_stock, Close_stock, Volume_stock,
         Return_stock, Return_rate_stock, exchangeShortName, marketSymbol, Open_market, High_market, 
         Low_market, Close_market, Volume_market, Adjusted, Return_market, Return_rate_market, Alpha,
         Beta, Expected_Return, Abnormal_Return, CAR_2day, mktCap, industry, sector, country,
         revenue, eps, reportedEPS, estimatedEPS, surprise, surprisePercentage, currentRatio, 
         returnOnAssets, returnOnEquity, debtRatio, CECR, PriceToBookR)

```


```{r}
# Run `final_df_sum for: final_df_section

# Create new column numerical quarter and yearQuarter variable
final_df_sum <- final_df_section %>%
  mutate(yearQuarterNumeric = year + (quarter - 1) / 4,
         yearQuarter = paste0(year, " Q", quarter))


# Region factor 
# Define the country codes for each region
north_america_codes <- c("US", "CA", "MX")
europe_codes <- c("GB", "DE", "FR", "IT", "ES", "NL", "CH", "SE", "NO", "BE", 
                  "AT", "IE", "PT", "FI", "DK", "GR", "CZ", "HU", "PL", "RO", 
                  "SK", "SI", "EE", "LV", "LT", "MT", "LU", "CY", "BG", "HR")
asia_codes <- c("JP", "CN", "IN", "KR", "ID", "VN", "TH", "PH", "MY", "SG", 
                "HK", "TW", "PK", "BD", "MM", "KH", "LA", "MO", "BN", "MV", 
                "BT", "NP", "TL", "MN")


# Create a new factor variable based on the country codes
final_df_sum <- final_df_sum %>%
  mutate(region = ifelse(country %in% north_america_codes, "North America",
                         ifelse(country %in% europe_codes, "Europe",
                                ifelse(country %in% asia_codes, "Asia", "Other"))))


# Convert the 'region', 'sector' and 'yearQuarter' columns to a factor
final_df_sum$region <- as.factor(final_df_sum$region)
final_df_sum$sector <- as.factor(final_df_sum$sector)
final_df_sum$yearQuarter <- as.factor(final_df_sum$yearQuarter)
final_df_sum$year <- as.factor(final_df_sum$year)

final_df_sum$region <- relevel(final_df_sum$region, ref = "Other")


# Tech dummy
final_df_sum$tech_dummy <- ifelse(final_df_sum$sector == "Technology", 1, 0)


# Convert to numeric variables
final_df_sum$reportedEPS <- as.numeric(final_df_sum$reportedEPS)
final_df_sum$estimatedEPS <- as.numeric(final_df_sum$estimatedEPS)
final_df_sum$surprise <- as.numeric(final_df_sum$surprise)
final_df_sum$surprisePercentage <- as.numeric(final_df_sum$surprisePercentage)


# AI disclosure (normalized)
final_df_sum <- final_df_sum %>% 
  mutate(AI_Main_n = (`AI_Main` / totalWordCount)*500,
         AI_QA_n = (`AI_QA` / totalWordCount)*500,
         RAI_Main_n = (`RAI_Main` / totalWordCount)*500,
         RAI_QA_n = (`RAI_QA` / totalWordCount)*500,
         AI_n = (AI / totalWordCount)*500,
         RAI_n = (RAI / totalWordCount)*500)


final_df_sum <- final_df_sum %>% 
  mutate(AI_words_Main_n = (`AI_words_Main` / totalWordCount)*500,
         AI_bigrams_Main_n = (`AI_bigrams_Main` / totalWordCount)*500,
         AI_words_QA_n = (`AI_words_QA` / totalWordCount)*500,
         AI_bigrams_QA_n = (`AI_bigrams_QA` / totalWordCount)*500,
         RAI_words_Main_n = (`RAI_words_Main` / totalWordCount)*500,
         RAI_bigrams_Main_n = (`RAI_bigrams_Main` / totalWordCount)*500,
         RAI_words_QA_n = (`RAI_words_QA` / totalWordCount)*500,
         RAI_bigrams_QA_n = (`RAI_bigrams_QA` / totalWordCount)*500)



```

---

**Select Data**

```{r}
# final_df_sum_section_select <- final_df_sum %>% 
#  select(-High_stock, -Low_stock, -Low_market, -High_market, -quarter, -AI_bigrams_Main,
#         -AI_bigrams_QA, -AI_words_Main, -AI_words_QA, -RAI_bigrams_Main, -RAI_bigrams_QA, -RAI_words_Main,
#         -RAI_words_QA, -AI_Main, -AI_QA, -RAI_Main, -RAI_QA , AI, RAI, -tech_dummy, -yearQuarterNumeric, -Alpha, -Beta, 
#         -Return_stock, - Return_market, -Expected_Return, -Adjusted, -Open_market, -Close_market, 
#         -Open_stock, -Open_market)


final_df_sum_section_select <- final_df_sum

```


**Normalizaiton**

*Market Cap*

```{r}
# Apply log transformation
final_df_sum_section_select <- final_df_sum_section_select %>%
  mutate(log_mktCap = log(mktCap))

# Calculate minimum and maximum values of the log_mktCap column
min_log_mktCap <- min(final_df_sum_section_select$log_mktCap)
max_log_mktCap <- max(final_df_sum_section_select$log_mktCap)

# Check if the minimum and maximum values are valid
cat("Minimum value:", min_log_mktCap, "\n")
cat("Maximum value:", max_log_mktCap, "\n")

# Apply normalization
final_df_sum_section_select <- final_df_sum_section_select %>%
  mutate(log_mktCap_norm = (log_mktCap - min_log_mktCap) / (max_log_mktCap - min_log_mktCap))

```

**Outliers**

```{r}
ggplot(data = final_df_sum_section_select, aes(y = log_mktCap_norm, x = CAR_2day)) +
  geom_point()

ggplot(data = final_df_sum_section_select, aes(y = CAR_2day, x = AI_n)) +
  geom_point()
ggplot(data = final_df_sum_section_select, aes(y = surprise, x = CAR_2day)) +
  geom_point()
ggplot(data = final_df_sum_section_select, aes(y = PriceToBookR, x = CAR_2day)) +
  geom_point()
ggplot(data = final_df_sum_section_select, aes(y = PriceToBookR, x = CAR_2day)) +
  geom_point()
ggplot(data = final_df_sum_section_select, aes(y = PriceToBookR, x = CAR_2day)) +
  geom_point()


```

```{r}
ggplot(data = final_df_sum_section_select, aes(y = CAR_2day)) +
  geom_boxplot()
```


**Winsorizing**

*Control variables*

```{r}
# controls 
final_df_sum_section_select$surprise <- Winsorize(final_df_sum_section_select$surprise, probs = c(0.05, 0.95), na.rm = T) 
final_df_sum_section_select$surprisePercentage <- Winsorize(final_df_sum_section_select$surprisePercentage, probs = c(0.05, 0.95), na.rm = T) 
final_df_sum_section_select$currentRatio <- Winsorize(final_df_sum_section_select$currentRatio, probs = c(0.05, 0.95), na.rm = T) 
final_df_sum_section_select$returnOnAssets <- Winsorize(final_df_sum_section_select$returnOnAssets, probs = c(0.05, 0.95), na.rm = T) 
final_df_sum_section_select$returnOnEquity <- Winsorize(final_df_sum_section_select$returnOnEquity, probs = c(0.05, 0.95), na.rm = T) 
final_df_sum_section_select$debtRatio <- Winsorize(final_df_sum_section_select$debtRatio, probs = c(0.05, 0.95), na.rm = T) 
final_df_sum_section_select$CECR <- Winsorize(final_df_sum_section_select$CECR, probs = c(0.05, 0.95), na.rm = T) 
final_df_sum_section_select$PriceToBookR <- Winsorize(final_df_sum_section_select$PriceToBookR, probs = c(0.05, 0.95), na.rm = T) 


```

## 4.3 Exploratory Analysis

### Summary statistics 

```{r}
mean(final_df_sum$totalWordCount)

```

```{r}
numeric_final_df_sum <- final_df_sum_section_select[sapply(final_df_sum_section_select, is.numeric)]
str(final_df_sum_section_select)
```


```{r}
# Re-scale volume_stock and volume_market
numeric_final_df_sum$Volume_stock <- numeric_final_df_sum$Volume_stock / 1e6
numeric_final_df_sum$Volume_market <- numeric_final_df_sum$Volume_market / 1e6
numeric_final_df_sum$mktCap <- numeric_final_df_sum$mktCap / 1e9
numeric_final_df_sum$revenue <- numeric_final_df_sum$revenue / 1e9

# Calculate summary statistics for the numeric_final_df_sum data frame
summary_stats <- data.frame(
  Variable = colnames(numeric_final_df_sum),
  N = sapply(numeric_final_df_sum, function(x) sum(!is.na(x))),
  Mean = sapply(numeric_final_df_sum, function(x) mean(x, na.rm = TRUE)),
  SD = sapply(numeric_final_df_sum, function(x) sd(x, na.rm = TRUE)),
  Min = sapply(numeric_final_df_sum, function(x) min(x, na.rm = TRUE)),
  Max = sapply(numeric_final_df_sum, function(x) max(x, na.rm = TRUE)),
  Median = sapply(numeric_final_df_sum, function(x) median(x, na.rm = TRUE))
)

stargazer(summary_stats, summary = FALSE, 
          title = "Summary Statistics", 
          type = 'latex',
          label = "tab:summary_stats",
          table.placement = "!htbp",
          header = FALSE,
          latex.options = "scale=0.75",
          column.labels = c("N", "Mean", "SD", "Min", "Max", "Median"))

```

```{r}
length(which(!is.na(numeric_final_df_sum$estimatedEPS)))
```


```{r}
# Get the list of variables in the data frame
variable_list <- names(final_df_sum_section_select)

# Print the list of variables
variable_list
```

### Transcript and AI count distribution

```{r}
# Calculate the summary statistics for the quarterNumeric column
summary_stats <- final_df %>%
#  filter(!is.na(year) & !is.na(quarter)) %>% 
  group_by(year, quarter) %>%
  summarise(count = n()) %>% 
  select(year, quarter, count) %>% 
  ungroup()

print(summary_stats)

# Display the summary statistics table using the stargazer package
stargazer(summary_stats, type = "latex", summary = FALSE, 
          title = "Summary Statistics: Quarter-Year and Transcripts",
          rownames = FALSE)
```


```{r}
library(xtable)
xtable(head(final_df), caption = "Head of final_df") %>%
  print(tex = "table")
```

### Transcript and AI word count distribution - per sector

```{r}
sector_summary <- final_df_sum %>%
  group_by(sector) %>%
  summarise(Count = n(),
            Sum_AI = sum(AI), 
            Sum_RAI = sum(RAI)) %>%
  rename(Sector = sector)

# Add a total row to the sector_summary data frame
sector_summary_with_total <- sector_summary %>%
  add_row(Sector = "Total",
          Count = sum(sector_summary$Count),
          Sum_AI = sum(sector_summary$AI),
          Sum_RAI = sum(sector_summary$RAI))

# Create a table with xtable
industry_table <- xtable(sector_summary_with_total, caption = "Sum of AI and RAI counts by Sector")
print(industry_table, include.rownames = FALSE, include.colnames = TRUE, floating = FALSE)

```

### Transcript and AI word count distribution - per yearQuarter

```{r}
# Summarize the data by yearQuarter
summary_df <- final_df_sum %>%
  group_by(yearQuarter) %>%
  summarize(AI_count = sum(AI),
            RAI_count = sum(RAI),
            transcript_count = n())


# Create the line and bar plot
plot_distribution_count <- ggplot() +
  geom_bar(data = summary_df, aes(x = yearQuarter, y = transcript_count), stat = "identity", alpha = 0.3, fill = "blue") +
  geom_line(data = summary_df, aes(x = yearQuarter, y = AI_count, color = "AI count", group = 1)) +
  geom_line(data = summary_df, aes(x = yearQuarter, y = RAI_count, color = "RAI count", group = 1)) +
  labs(
    # title = "AI and RAI Word Count and Transcript Distribution over Time",
       x = "Date",
       y = "Count",
       color = "Legend") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom")  # Move the legend to the bottom


# Save the plot as a PNG file
ggsave("Output/plot_distribution_count.png", plot_distribution_count, width = 10, height = 6, dpi = 300)

```

### Transcript and AI word count distribution - per region

```{r}
region_summary <- final_df_sum %>%
  group_by(region) %>%
  summarise(Count = n(),
            `AI count` = sum(AI), 
            `RAI count` = sum(RAI)) %>%
  rename(Region = region)

# Add a total row to the region_summary data frame
region_summary_with_total <- region_summary %>%
  add_row(Region = "Total",
          Count = sum(region_summary$Count),
          `AI count` = sum(region_summary$`AI count`),
          `RAI count` = sum(region_summary$`RAI count`))

# Create a table with xtable
region_table <- xtable(region_summary_with_total, caption = "Sum of AI and RAI counts by Region")
print(region_table, include.rownames = FALSE, include.colnames = TRUE, floating = FALSE)

```


## 4.4 CAR relationships  

### Correlation plot


```{r}
# Select required columns
selected_df <- final_df_sum_section_select[c("CAR_2day", "AI_Main_n", "AI_QA_n", "RAI_Main_n", "RAI_QA_n", "surprise", "log_mktCap")]

# Exclude rows with missing values
complete_data <- selected_df[complete.cases(selected_df), ]

# Create correlation matrix
cor_mat <- round(cor(complete_data), 2)

# Create p-value matrix
p_mat <- round(cor.mtest(complete_data)$p, 3)

# Create correlation plot
corrplot(cor_mat, p.mat = p_mat, insig = "blank", method = "color", diag = FALSE)

# Set upper triangular part to NA
cor_mat[upper.tri(cor_mat)] <- NA
p_mat[upper.tri(p_mat)] <- NA

# Add significance levels as asterisks
for(i in 1:nrow(cor_mat)) {
  for(j in 1:ncol(cor_mat)) {
    if(!is.na(p_mat[i,j])) {
      if(p_mat[i,j] < 0.01) {
        cor_mat[i,j] <- paste(cor_mat[i,j], "***")
      } else if(p_mat[i,j] < 0.05) {
        cor_mat[i,j] <- paste(cor_mat[i,j], "**")
      } else if(p_mat[i,j] < 0.1) {
        cor_mat[i,j] <- paste(cor_mat[i,j], "*")
      }
    }
  }
}

# Create table with xtable
tab <- xtable(cor_mat, caption = "Correlation matrix with significance levels")
print(tab, include.rownames = TRUE, include.colnames = TRUE, floating = FALSE, sanitize.text.function = function(x) {x})

# Add title and significance level labels
cat("\nSignificance levels:\n")
cat("  '***' 0.01\n  '**' 0.05\n  '*' 0.1\n")

```

Analysis steps (Before regression)

### Regression output

Other control variables: 
- country + Alpha + Beta + Expected_Return + revenue

```{r}
# Create the regression table
model_all <- lm(CAR_2day ~ AI_n + RAI_n + surprise
                  + currentRatio + returnOnAssets + returnOnEquity + debtRatio + 
                    CECR + PriceToBookR + log_mktCap_norm, data = final_df_sum_section_select)
model_split <- lm(CAR_2day ~ AI_Main_n + AI_QA_n + RAI_Main_n + RAI_QA_n + surprise
                  + currentRatio + returnOnAssets + returnOnEquity + debtRatio + 
                    CECR + PriceToBookR + log_mktCap_norm, data = final_df_sum_section_select)

model_split_2 <- lm(CAR_2day ~ AI_Main_n + AI_QA_n + RAI_Main_n + RAI_QA_n + surprise
                  + currentRatio + returnOnAssets + returnOnEquity + debtRatio + 
                    CECR + PriceToBookR + log_mktCap_norm, data = final_df_sum_section_select)




# Output table
stargazer(model_all, model_split, type = 'text', no.space = TRUE) # 


```

Robustness checks

Tech only sector that has positive effect on CAR

```{r}
model_region <- lm(CAR_2day ~ AI_Main_n + AI_QA_n + RAI_Main_n + RAI_QA_n + surprise
                  + currentRatio + returnOnAssets + returnOnEquity + debtRatio + 
                    CECR + PriceToBookR + log_mktCap_norm  + factor(region)
                  , data = final_df_sum_section_select)

model_tech <- lm(CAR_2day ~ AI_Main_n + AI_QA_n + RAI_Main_n + RAI_QA_n + surprise
            + currentRatio + returnOnAssets + returnOnEquity + debtRatio
            + CECR + PriceToBookR + log_mktCap_norm 
            + factor(tech_dummy), data = final_df_sum_section_select)

model_tech_interaction <- lm(CAR_2day ~ AI_Main_n*tech_dummy + AI_QA_n*tech_dummy + 
                               RAI_Main_n*tech_dummy + RAI_QA_n*tech_dummy + surprise
                             + currentRatio + returnOnAssets + returnOnEquity + debtRatio 
                             + CECR + PriceToBookR + log_mktCap_norm, data = final_df_sum_section_select)


final_df_prior_2021 <- subset(final_df_sum_section_select, year %in% c("2017", "2018"))

model_tech_2021 <- lm(CAR_2day ~ AI_Main_n + AI_QA_n + RAI_Main_n + RAI_QA_n + surprise
            + currentRatio + returnOnAssets + returnOnEquity + debtRatio
            + CECR + PriceToBookR + log_mktCap_norm + factor(tech_dummy), data = final_df_prior_2021)




stargazer(model_region, model_tech, model_tech_interaction, model_tech_2021, omit = c("currentRatio", "returnOnAssets", "returnOnEquity",
                          "debtRatio", "CECR", "PriceToBookR"),
           no.space = TRUE, type = 'latex')

```



### Robustness Checks

```{r}
fitted_values <- fitted(model_split)
residuals <- resid(model_split)
plot(fitted_values, residuals, main="Residuals vs Fitted", 
     xlab="Fitted values", ylab="Residuals", pch=19, col="blue")
abline(h=0, lty=2, col="red") # adds a horizontal line at zero

```

```{r}
install.packages("car")
library(car)
vif(model_split)

```

```{r}
bptest(model_split)
```


